---
title: "Azores Spasm: Movement"
author: "Ian"
date: "February 5, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
source('../R/move_fish_az.R')
#boxdir<-"/Users/lennonrosethomas/Box Sync/SFG Centralized Resources/Projects/BPC/Azores/data/bsb_model/"
boxdir <- "C:/Users/iladner/Box/SFG Centralized Resources/Projects/BPC/Azores/data/bsb_model/"
#boxdir <- "C:/Users/ianla/Box/SFG Centralized Resources/Projects/BPC/Azores/data/bsb_model/"
runname <- "test"

juve_distance<-read.csv(paste0(boxdir,runname,"/juve_distance.csv"))
adult_distance<-read.csv(paste0(boxdir,runname,"/adult_adult_distance.csv"))
juve_adult_distance<-read.csv(paste0(boxdir,runname,"/juve_adult_distance.csv"))
adult_juve_distance<-read.csv(paste0(boxdir,runname,"/adult_juve_distance.csv"))
juve_distance<-read.csv(paste0(boxdir,runname,"/juve_distance.csv"))
shore_dist<-read.csv(paste0(boxdir,runname,"/distance_to_shore.csv"))

hab_qual<-c(.5,.05,.05,.05,0.05,0.05,0.05,0.05,0.05,.1,rep(0,10))
num_patches<-length(unique(adult_distance$from))
# Create dataframe that has cell_no, patch_no, whether juve or adult, and habitat quality


cell_lookup<-data.frame(matrix(ncol=4,nrow=num_patches))
colnames(cell_lookup)<-c("patch","cell_no","juve_ad_hab","hab_qual")
cell_lookup[,1]<-c(1:20)
cell_lookup[,2]<-unique(adult_distance$from)
cell_lookup[,3]<-c(rep(0,10),rep(1,10))
cell_lookup[,4]<- hab_qual<-c(.5,.05,.05,.05,0.05,0.05,0.05,0.05,0.05,.1,rep(0,10))# Adult habitat quality

### read in example pop taken from year two of sim_fishery_az
pop <- read_csv("../data/pop_example.csv")
ssb0 <- read_csv("../data/example_ssb0.csv")$value
```

## Parameter: adult_movement

The `adult_movement` parameter helps determine the degree to which fish disperse to other patches. The absolute value isn't what's important here, it's the value of adult_movement parameter relative to the distance between adult habitat patches. When density-dependence is not included in the model, fish are redistributed from a patch to others using the following steps:

* The distance between two patches is checked against a normal distriubtion with a mean of 0 and a standard deviation of `adult_movement`. The value (f(x)) of the normal distribution curve at that point is saved for each combination of patches.
* For all the mature fish in a given patch, they redistribute to other **adult** (check with LT) habitat patches with the probability of the value calculated above divided by the sum of the values for each possible movement combinations from the patch in question to all other adult patches (including itself). This creats a dataframe as follows:

Using `adult_movement = 100`

```{r adult_movement base case}
adult_movement <- 100

adult_move_grid_independent <- adult_distance %>%
  left_join(cell_lookup, by = c("to" = "cell_no"))%>%
  dplyr::mutate(movement = ifelse(is.na(dist), NA, ifelse(
    is.finite(dnorm(dist, 0, adult_movement)),
    dnorm(dist, 0, adult_movement),
    1
  )))%>%
  group_by(from) %>%
  dplyr::mutate(prob_move = movement / sum(movement, na.rm = TRUE))

adult_move_matrix_independent <- adult_move_grid_independent %>%
  ungroup() %>%
  dplyr::select(from, to, prob_move) %>%
  spread(to, prob_move) %>%
  dplyr::select(-from) %>%
  #  uncount(10) %>%
  as.matrix()

adult_move_matrix_independent[is.na(adult_move_matrix_independent)] <- 0

base_case_table <- adult_move_grid_independent %>% 
  filter(from == 410, !is.na(dist)) %>% 
select(from, to, dist, prob_move) %>% 
  arrange(dist)
```

```{r base_case_table, results = "asis"}
knitr::kable(base_case_table)
```

* In this example, where `adult_movement` is on the same order of magnitude but smaller than the distance between the selected patch and it's nearest neightbor, we would see roughly half of the adults stay put and the other half redistribute to the other patches.  The three furthest patches (where `dist` > `4 * adult_movement`) recieve almost zero immigrants from the selected patch.

* As `adult_movement` increases,  so does the standard distribution of the curve used to calculate probabilty. This places the patches relatively closer together in space in the context of the movement of the fish. Therefore, as `adult_movement` increases to and beyond the value of `max(dist)` for a given patch, we would expect a more even distribution of fish from that patch to all others.

* In the current paramter space, the two closest patches are `r min(filter(adult_distance, dist > 0)$dist)` units apart and the farthest distance between two patches is `r max(adult_distance$dist, na.rm = T)` units. 

*The sensitivity of fish in a selected patch to the value of `adult_movement` can be seen below:

```{r adult_movement sensitivity analysis}
movement_table <- base_case_table %>% 
  mutate(adult_movement = 100)


adult_movement_vector <- c(50,250,500,1000)


for(i in 1:length(adult_movement_vector)){
  adult_movement_temp <- adult_movement_vector[i]
  
  movement_table_temp <- adult_distance %>%
  left_join(cell_lookup, by = c("to" = "cell_no"))%>%
  dplyr::mutate(movement = ifelse(is.na(dist), NA, ifelse(
    is.finite(dnorm(dist, 0, adult_movement_temp)),
    dnorm(dist, 0, adult_movement_temp),
    1
  )))%>%
  group_by(from) %>%
  dplyr::mutate(prob_move = movement / sum(movement, na.rm = TRUE)) %>% filter(from == 410, !is.na(dist)) %>% 
select(from, to, dist, prob_move) %>% 
  arrange(dist) %>% 
  mutate(adult_movement = adult_movement_temp)
  
  movement_table <- rbind(movement_table, movement_table_temp)
}

ggplot(movement_table, aes(x = dist, y = prob_move, color = as.factor(adult_movement)))+
    geom_line()+
  geom_point()+
  theme_classic()+
  labs(y = "Probability of moving", x = "Distance to patch", color = "Value of adult_movement", title = "Movement away from patch 410")
```

```{r add plot of ssb before and after movement, include = F}
pop_before_movement <- pop %>% 
  filter(year == 2, age > 4) %>% 
  mutate(timing = "before movement")

pop_after_movement <-
  move_fish_az(
    here_pop = pop_before_movement,
    fish = NA,
    num_patches = 20,
    move_matrix = adult_move_matrix_independent
  ) %>% mutate(timing = "after movement")


rbind(pop_before_movement,pop_after_movement) %>% 
  group_by(patch, timing) %>% 
  summarize_at(c("numbers","biomass","ssb"), sum) %>% 
  ungroup() %>% 
  filter(patch <= 10) %>% 
  ggplot(aes(x = as.factor(patch), y = ssb, fill = fct_relevel(timing, "before movement", "after movement")))+
  geom_col(position = "dodge")+
  labs(fill = "", x = "patch")+
  theme_classic()

``` 

### How does this play out across all patches?

We can vary the value of `adult_movement` to see how it affects the system on a whole.

```{r same as above, but now loop through multiple values of }

ssb_movement_example <- tibble()

ssb_movement_vector <- c(50,100,500,1000)

for(m in 1:length(ssb_movement_vector)){
  pop_before_movement <- pop %>% 
  filter(year == 2, age > 4) %>% 
  mutate(timing = "before movement")
  
  
  move_matrix_temp <- adult_distance %>%
  left_join(cell_lookup, by = c("to" = "cell_no"))%>%
  dplyr::mutate(movement = ifelse(is.na(dist), NA, ifelse(
    is.finite(dnorm(dist, 0, ssb_movement_vector[m])),
    dnorm(dist, 0, ssb_movement_vector[m]),
    1
  )))%>%
  group_by(from) %>%
  dplyr::mutate(prob_move = movement / sum(movement, na.rm = TRUE)) %>%
  ungroup() %>%
  dplyr::select(from, to, prob_move) %>%
  spread(to, prob_move) %>%
  dplyr::select(-from) %>%
  as.matrix()

move_matrix_temp[is.na(move_matrix_temp)] <- 0

pop_after_movement <-
  move_fish_az(
    here_pop = pop_before_movement,
    fish = NA,
    num_patches = 20,
    move_matrix = move_matrix_temp
  ) %>% mutate(timing = "after movement")

pop_temp <- rbind(pop_before_movement,pop_after_movement) %>% 
  mutate(adult_movement = ssb_movement_vector[m])

ssb_movement_example <- rbind(ssb_movement_example, pop_temp)
}

ssb_movement_example %>% group_by(adult_movement,patch, timing) %>% 
  summarize_at(c("numbers","biomass","ssb"), sum) %>% 
  ungroup() %>% 
  filter(patch <= 10) %>% 
  ggplot(aes(x = as.factor(patch), y = ssb, fill = fct_relevel(timing, "before movement", "after movement")))+
  geom_col(position = "dodge")+
  labs(fill = "", x = "patch")+
  theme_classic()+
  facet_wrap(~adult_movement)

#ggsave("ssb_with_movement_example.png")

```

This figure shows the ssb for each patch before and after movement for four different values of adult_movement: 50, 100, 500, 1000. There is very little redistribution when it equals 50 (near the minimum distance between patches) and almost completely even redistribution when it hits 1000 (greater than twice the max distance between patches).


## Parameter: density_movement_modifier

Density-dependent movement allows the density of fish in a given patch to modulate the rate at which fish leave that patch. The inuition here is that as density increases ("more crowded"), fish will be more likely to move away from that patch in search of less competition elsewhere. Density-dependent movement introduces two additional variables/factors:

* `depletion`: The ssb of the patch in that year relative to ssb0. Ranges from 0 (fully depleted) to values above 1 (more ssb than in year 0). Not explicitly defined in parameter space, but calculated internally by the model.
* `density_movement_modifier`: The degree to which fish are "sensitive" to crowding. As.....

```{r lets figure this out for density-dependent-movement}
dens_dependent_example <- tibble()

dens_modifier_vector <- c(0,0.5,0.99)

adult_movement <- 100

for(index in 1:length(dens_modifier_vector)){

  pop_before_movement <- pop %>% 
  filter(year == 2, age > 4) %>% 
  mutate(timing = "before movement")
  
  slope <-
  adult_movement - (adult_movement * dens_modifier_vector[index])

how_crowded <- pop %>%
  group_by(patch) %>%
  summarise(ssb = sum(ssb, na.rm = TRUE)) %>%
  dplyr::arrange(patch) %>%
  mutate(depletion = ssb / ssb0) %>%
  mutate(move_rate = pmin(
    adult_movement,
    slope * depletion + (adult_movement * dens_modifier_vector[index])
  )) %>%
  dplyr::select(patch, move_rate) %>% 
  left_join(cell_lookup) %>%
  dplyr::select(cell_no, move_rate)

move_matrix_temp <- adult_distance %>%
  left_join(how_crowded, by = c("from" = "cell_no")) %>%
  dplyr::mutate(movement = ifelse(is.na(dist), NA, ifelse(
    is.finite(dnorm(dist, 0, move_rate)),
    dnorm(dist, 0, move_rate),
    1
  )))  %>%
  group_by(from) %>%
  dplyr::mutate(prob_move = movement / sum(movement,na.rm = TRUE))%>%
  ungroup()%>%
  dplyr::select(from, to, prob_move) %>%
  spread(to, prob_move) %>%
  dplyr::select(-from) %>%
    as.matrix()
 
move_matrix_temp[is.na(move_matrix_temp)] <- 0

pop_after_movement <-
  move_fish_az(
    here_pop = pop_before_movement,
    fish = NA,
    num_patches = 20,
    move_matrix = move_matrix_temp
  ) %>% mutate(timing = "after movement")

pop_temp <- rbind(pop_before_movement,pop_after_movement) %>% 
  mutate(rho = dens_modifier_vector[index])

dens_dependent_example <- rbind(dens_dependent_example, pop_temp)
}

dens_dependent_example %>%  group_by(rho,patch, timing) %>% 
  summarize_at(c("numbers","biomass","ssb"), sum) %>% 
  ungroup() %>% 
  filter(patch <= 10) %>% 
  ggplot(aes(x = as.factor(patch), y = ssb, fill = fct_relevel(timing, "before movement", "after movement")))+
  geom_col(position = "dodge")+
  labs(fill = "", x = "patch")+
  theme_classic()+
  facet_wrap(~rho)

```

